---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# xaringancolor

<!-- badges: start -->
<!-- badges: end -->

The goal of xaringancolor is to allow you to change the colors uniformly across text, equations, and code.

## Installation

You can install the package with:

``` r
# install.packages("devtools")
devtools::install_github("EmilHvitfeldt/augassign")
```

This package will most likely never be put on CRAN.

## How to setup

xaringancolor only contain 1 function; `setup_colors()`. Pass the colors you want to use in as named arguments. Please be careful and use simple names, preferably letters only, no numbers, spaces, or other characters.

```{r, eval=FALSE}
library(xaringancolor)
setup_colors(
  orange = "#EF8633",
  blue = "#3381F7",
  red = "red"
)
```

Running this code includes some lines of code into your clipboard. Paste this into the beginning of your [xaringan](https://github.com/yihui/xaringan) document. After you have done that you can delete the above code, you won't be needing it anymore.

## How to use

### HTML

css classes named according to the colors have been created, so if you want some text to be red you type `.red[my text]` and text inside the square brackets turn red. This only works for the colors you have created and you need to put a leading period (.) before the color name when you use the css class.

### Equations

A LaTeX macro has been created for each color. Use them as follows

```{code, eval=FALSE}
$$\orange{Y} = a \blue{X} + b$$
```

and `Y` will be colored orange and `X` will be colored blue.

### Code

A variable for each color has been created. These can be used directly in plots such as with `geom_abline(..., color = orange)` but they can also be used with **flair**.

Start with a named chunk with both `include` and `eval` set to `FALSE`. This is the code you want to highlight

```code
``{r mtcars_mean, include=FALSE, eval=FALSE}
lapply(mtcars, mean)
``
```

then you add another chunk with `echo=FALSE` where you use the `decorate()` to select the previous chunk by name and `flair()` to denote which parts of the code should be colors which way. Use the color variables here to achieve uniform coloring throughout the presentation.

```code
``{r, echo=FALSE}
decorate("mtcars_mean") %>%
  flair("mtcars", color = orange) %>%
  flair("mean", color = blue)
``
```

See [this link](https://r-for-educators.github.io/flair/index.html) for more information on how to use **flair**.

## How it works

The code will look something like the code below and serve 3 main purposes. The first section defines the LaTeX colors and the second section uses [Mathjax](https://www.mathjax.org/) to generate LaTeX macros which allow us to use colors in the equations.

```code

$$\require{color}\definecolor{orange}{rgb}{0.937254901960784, 0.525490196078431, 0.2}$$
$$\require{color}\definecolor{blue}{rgb}{0.2, 0.505882352941176, 0.968627450980392}$$
$$\require{color}\definecolor{red}{rgb}{1, 0, 0}$$

<script type="text/x-mathjax-config">
MathJax.Hub.Config({
  TeX: {
    Macros: {


     orange: ["{\\color{orange}{#1}}", 1],

     blue: ["{\\color{blue}{#1}}", 1],

     red: ["{\\color{red}{#1}}", 1]


  },
    loader: {load: ['[tex]/color']},
    tex: {packages: {'[+]': ['color']}}
  }
});
</script>

```

The third section defines a \<style\> tag with sets the colors so we can use them in the html text.

```code

<style>
.orange {color: #EF8633;}
.blue {color: #3381F7;}
.red {color: #FF0000;}
</style>

```

And the fourth and final section creates a R chunk that sets us up to use [flair](https://github.com/r-for-educators/flair) package. It loads the package and defines character vectors that specify the colors.

```code

``{r flair_color, echo=FALSE}
library(flair)
orange <- "#EF8633"
blue <- "#3381F7"
red <- "#FF0000"
``

```
